Our Future Nuclear Data Needs

### 2018-12-16 nuclear_data_needs/nuclear_data_needs.tex
Fixed page margins (somewhat_

\documentclass[letterpaper]{ar-1col}
\usepackage[numbers]{natbib}

\usepackage[american]{babel}
% \usepackage{amsmath}
% \usepackage[version=3]{mhchem} 
% % \usepackage{fixltx2e}
% % \usepackage{refcount}
% % \usepackage{siunitx}
% % \usepackage{lastpage}
% % \usepackage{textcomp}
% \usepackage{mathtools}
% 
% \usepackage{xfrac}
% \usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% % \usepackage{cool}
% % \usepackage{cancel}
% % \usepackage{microtype}
% \usepackage{listings}
% % \usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% % \usepackage{longtable}
% % \usepackage{subcaption}
% \usepackage{booktabs,siunitx}
% \usepackage{gensymb}
% \usepackage[normalem]{ulem}

@@

% \usepackage[style=base]{caption}
\usepackage{subfig}
% Remove a), b), etc labels from subfigs
\captionsetup[subfigure]{labelformat=empty}
% \captionsetup{style=base}

@@

%Abstract
\begin{abstract}
Abstract text, approximately 150 words. 
\end{abstract}

>>>>

\documentclass[letterpaper,draft]{ar-1col}
\usepackage[numbers]{natbib}
\usepackage[left=35mm,top=26mm,right=26mm,bottom=15mm]{geometry}

\usepackage[american]{babel}
% \usepackage{amsmath}
% \usepackage[version=3]{mhchem} 
% % \usepackage{fixltx2e}
% % \usepackage{refcount}
% % \usepackage{siunitx}
% % \usepackage{lastpage}
% % \usepackage{textcomp}
% \usepackage{mathtools}
% 
% \usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% % \usepackage{cool}
% % \usepackage{cancel}
% % \usepackage{microtype}
% \usepackage{listings}
% % \usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% % \usepackage{longtable}
% % \usepackage{subcaption}
% \usepackage{booktabs,siunitx}
% \usepackage{gensymb}
% \usepackage[normalem]{ulem}

@@

% \usepackage[style=base]{caption}
% \usepackage{subfig}
% Remove a), b), etc labels from subfigs
% \captionsetup[subfigure]{labelformat=empty}
% \captionsetup{style=base}

@@

%Abstract
\begin{abstract}
A well-established knowledge of nuclear phenomena including fission, reaction cross sections, and structure/decay properties, is critical for applications ranging from the design of new reactors, to non-proliferation, to the production of radioisotopes for the diagnosis and treatment of illness.  However, the lack of a well-quantified, predictive theoretical capability means that most nuclear observables must be measured directly in order to “calibrate” empirical models, which, in turn, provide the data needed for these applications.  In many cases there is either a lack of the data needed to guide the models, or the results of the different measurements are discrepant.  This has led to the development of evaluation methodologies to provide recommended values and uncertainties.  In this article we present the nuclear data evaluation process and the international community that carries it out.  We then discuss new measurements and improved theory and/or modeling needed to address future challenges in applied nuclear science. 
\end{abstract}
